\LARGE \bf Minimum Uncertainty JPDA Filter and Coalescence Avoidance

### 2018-06-09 Conference/AAS 2015 DA/ACC 2015/ACC15_Final.tex
added Conference folder

\title{\LARGE \bf
%Systematic Reduction of Uncertainty and Coalescence from JPDA Filtering
%Minimum Uncertainty JPDA Filtering and Advancements on Avoiding Coalescence
Minimum Uncertainty JPDA Filter and Coalescence Avoidance}
\author{Evan Kaufman, Thomas Alan Lovell, and Taeyoung Lee$^*$
 \thanks{Evan Kaufman and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{evankaufman, tylee\}@gwu.edu }}
\thanks{Thomas Alan Lovell is a Research Aerospace Engineer at the Space Vehicles Directorate, Air Force Research Lab (AFRL), Albuquerque, NM. Email: {\tt\footnotesize afrl.rvsv@kirtland.af.mil }}
\thanks{$^*$This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}}

@@

Data association has been extensively studied with various applications in estimation when measurements are not necessarily originating from a single object.
We consider applications wherein multiple objects of interest enter the field of view of a sensor; however, the measurement origins are unknown.
To properly track these objects, we require estimation techniques that associate objects with measurements.
When the objects are in very close proximity, the association uncertainties grow, and an effective algorithm is necessary to maintain close estimations of the objects~\cite{KauLovLee14}.

@@

Alternatively with a soft decision technique such as the JPDAF, measurements are shared among the estimates. With the JPDAF, the likelihoods of association between measurements and estimates serve as weighting factors inside the measurement update portion of the filtering~\cite{JPDAF1},~\cite{TrackDataAssoc}.
The JPDAF is particularly advantageous in multi-object scenarios because when objects share measurements, the soft decisions prevent loss of information, which occurs with hard decision approaches.
%The a posteriori uncertainties of the estimates are changed because of an additional term representing the spread in the innovations; the Kalman gain serves as a close estimate to an optimal gain in the sense that in nearly minimizes this a posteriori gain as derived by the linearized equations of the JPDAF.
The JPDAF is based on the Kalman gain, which minimizes the posterior uncertainty of individual tracks.
However, the Kalman gain is not guaranteed to \emph{exactly} minimize the posterior uncertainties of the JPDAF.
%The unnecessarily large uncertainty of the suboptimal Kalman gain serves as motivation to derive an optimal gain that minimizes the a posteriori uncertainty of the linearized JPDAF equations.
In this paper, we derive the optimal estimation gain that minimizes the magnitude of the posterior covariance matrix, and the resulting minimum uncertainty JPDAF is referred to as the MUJPDAF.

@@

Therefore, we propose a new coalescence-avoiding optimal JPDAF referred to as the C-JPDAF, which is a systematic approach to remove coalescence by minimizing the weighted sum of the uncertainty and a similarity index between estimates~\cite{KauLovLee14}.
The prior research covers the concept in simple cases, such that only two estimates are considered with a single measurement at each time step, making the algorithm infeasible in many realistic applications.
Therefore, we generalize the algorithm to handle any number of objects and measurements, as well as missed detections and measurements originating from extraneous clutter.
%Therefore we mature the algorithm to have the same assumptions as the JPDAF.
%Most importantly, there may be a variable number of measurements for a known number of estimates such that missed detections and false alarms are no longer an issue.

@@

During the flow update, the a priori (denoted with superscript $-$) estimated state $\hat x_{i_k}^-$ is found with \refeqn{xkp} and its a priori covariance $P_{i_k}^-$ is calculated from the last posterior (denoted with superscript $+$) covariance $P_{i_{k-1}}^+$ for all $i$ as
\begin{gather}
%\hat x_{i_{k}}^- = f(\hat x_{i_{k-1}}^+),\\
P_{i_{k}}^- = F_{i_{k-1}} P_{i_{k-1}}^+ F_{i_{k-1}}^T + Q_{i_{k}}.
\end{gather}
These equations are applied between measurements to provide predictions of the states and their uncertainties.
% Equations for a priori state estimates and covariances

@@

The optimal gain $K_i$ is derived below in the sense that the posterior uncertainties are minimized with respect to the generalized equations of the JPDAF.

@@

Let the probability that object $i$ is not associated with any measurement be $\beta_{0,i}=1-{\sum\limits_{j} \beta_{ij}}$.
The resulting posterior covariance can be written as
%~\cite[Eq. D-32 and D-33]{TrackDataAssoc}
\begin{align}
\label{eqn:JPDAFCov}
P^+_{i}=&\ \beta_{0,i}P^-_{i}+(1-\beta_{0,i})P_i^c+\tilde P,
\end{align}
where $\tilde P\in\Re^{n\times n}$ is
\begin{align}
\tilde P=&\ K_i\left({\sum\limits_{j} \beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}}{\bf{e}}_{i}^T\right)K_{i}^T,\label{eqn:tildeP}
\end{align}
and $P_i^c$ corresponds to the posterior covariance of object $i$ if only a single measurement serves to update this track~\cite{TrackDataAssoc}, and it can be written as
%We can define $P_i^c$ without any assumptions on $K_i$ (i.e. $K_i$ is not necessarily the Kalman gain, so the well-known Kalman covariance update equations are not valid here) as~\cite[Eq. 4.2-12]{OptEst1}
\begin{align}
P^c_i=&\ (I-K_iH_i)P^-_i(I-K_iH_i)^T+K_iR_iK_i^T,\nonumber
\\
=&\ P^-_i-(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_i(H_iP^-_iH_i^T+R_i)K_i^T,
\label{eqn:GenCov}
\end{align}
(see~\cite{OptEst1}).
Substituting \refeqn{tildeP} and \refeqn{GenCov} into \refeqn{JPDAFCov} and rearranging,
\begin{align}
P^+_{i}=&\ \beta_{0,i}P^-_{i}+(1-\beta_{0,i})[P^-_i-(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_i(H_iP^-_iH_i^T+R_i)K_i^T]\nonumber
\\
&\ +K_i\left({\sum\limits_{j} \beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}}{\bf{e}}_{i}^T\right)K_{i}^T,\nonumber
\\
=&\ P^-_{i}-(1-\beta_{0,i})(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_i\left((1-\beta_{0,i})S_i+{\sum\limits_{j} \beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}}{\bf{e}}_{i}^T\right)K_i^T,\nonumber
\\
=&\ P^-_{i}-(1-\beta_{0,i})(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_iE_iK_i^T,\label{eqn:CovExpanded}
\end{align}
where the symmetric matrix $E_i=E_i^T\in\Re^{m\times m}$, defined as
\begin{align}
E_i=&\ (1-\beta_{0,i})S_i+{\sum\limits_{j} \beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}}{\bf{e}}_{i}^T.
\end{align}
Note that $E_i$ is independent of $K_i$ and is invertible when $\beta_{0,i}\neq1$ since $S_i$ is positive-definite and
%may be calculated without knowledge of the gain matrix $K_i$, and is invertible because $P^-_i$ and $R_i$ are positive-definite and
$(\beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}{\bf{e}}_{i}^T)$ is positive-semidefinite, as shown in the Appendix A. 
The case when $\beta_{0,i}=1$ corresponds with the $i$-th object \emph{not} being measured with full certainty.
This case is analyzed in Appendix B.

@@

Finally, \refeqn{GainK} is substituted into \refeqn{CovExpanded} to obtain
\begin{align}
%\begin{split}
%P^+_{i}=&P^-_{i}-(1-\beta_{0,i})^2(P^-_iH_i^TE_i^{-1}H_iP^-_i
%\\
%&+P^-_iH_i^TE_i^{-1}H_iP^-_i
%-P^-_iH_i^TE_i^{-1}E_iE_i^{-1}H_iP^-_i)
%\end{split}
%\\
P^+_{i}=&P^-_{i}-(1-\beta_{0,i})^2P^-_iH_i^TE_i^{-1}H_iP^-_i,
\end{align}
which may be simplified in two ways
\begin{align}
P^+_{i}=&P^-_{i}-K_iE_iK_i^T, \quad \mbox{or equivalently}\label{eqn:JPDAFPostCovSymmetricUpdate}
\\
P^+_{i}=&\left(I-(1-\beta_{0,i})K_iH_i\right)P^-_i.\label{eqn:JPDAFPostCovSimpleUpdate}
\end{align}
The proposed gain is compared with the Kalman gain explicitly in Appendix C.
In short, the differences between the MUJPDAF and the conventional JPDAF are shown in \refeqn{GainK} and \refeqn{JPDAFPostCovSymmetricUpdate} or \refeqn{JPDAFPostCovSimpleUpdate}.

@@

The Matusita's similarity measure is defined between two Gaussian distributions.
Let $y_i$ be a random variable corresponding to the $i$-th system of set $I$ such that $y_i \sim \mathcal{N}[\hat y_i,{\mathbf P}_i]$, and let indices $p,q\in I$ such that $p\neq q$.
From~\cite{KauLovLee14}, the portion of the Matusita's similarity measure corresponding to the spread in the estimate means is given by
\begin{align}
\zeta_{pq}=\exp \{-a(y_{p}- y_{q})^T({\mathbf P}_{p}
+{\mathbf P}_{q})^{-1}(y_{p}-y_{q})\},\label{eqn:Mat2Est}
\end{align}
where $a>0$ shapes the similarity measure.

However, the distributions of more than two estimates may exhibit a nonzero overlap.
The similarity measure is changed to suit \emph{any} number of estimates by summing all combinations of Matusita's similarity measures, illustrated in Figure \ref{fig:SimMeas}, expressed in a general sense as
\begin{align}
\zeta=\sum\limits_{p,q\in I,p\neq q}\exp \{-a(y_{p}- y_{q})^T({\mathbf P}_{p}
+{\mathbf P}_{q})^{-1}(y_{p}-y_{q})\},
\end{align}
which is the summation of every similarity measure from \refeqn{Mat2Est} between all different Gaussian distributions $y_i$.
\begin{figure}
\centerline{
		{\includegraphics[width=\columnwidth]{GaussianDistOverlap1D.png}}
	}
\caption{The similarity index between three Gaussian distributions is a function the summation measures of overlapping regions of two distributions (green) or three distributions (brown). This concept is easily extended to multivariate distributions.
}\label{fig:SimMeas}
\end{figure}

@@

\paragraph*{Similarity Cost}
Any shared $z_j$ on estimate $i$ yields an innovation $e_{ij}$.
During the measurement update, this innovation typically has the net effect of drawing the measurement estimate towards $z_j$ if $\beta_{ij}$ is nonzero.
This occurs for all estimates and all measurements; coalescence results when measurement estimates are drawn towards common measurements.
Therefore, coalescence of the JPDAF or MUJPDAF occurs inside the measurement space (e.g. if a sensor provides ranges and bearings, these are in the measurement space as opposed to a Cartesian state vector inside the state space).
Contrary to~\cite{KauLovLee14} where the similarity index is in terms of state space variables, the coalescence avoidance presented in this paper takes place inside the measurement space to most directly remove the coalescence.
Let the posterior measurement estimate be $\hat z_i^+\in\Re^m$ and its innovation be $e_{i}^+\in\Re^m$ that corresponds with its true measurement $z_i\in\Re^m$ (although association is unknown) as
\begin{align}
\hat z_i^+&=H_i\hat x_i^+,
\\
e_{i}^+&=z_i-\hat z_i^+=(H_ix_i+v_i)-H_i\hat x_{i}^+=H_i\tilde x_i^++v_i,
\end{align}
where $\tilde x_i^+=x_i-\hat x_{i}^+$ denotes the error between the true state and the posterior estimate. The posterior innovation covariance $S^+_i\in\Re^{m\times m}$ is given by
\begin{align}
S^+_i&=\mathrm{E}[e_i^+e_i^{+T}]=\mathrm{E}[(H_i\tilde x_i^++v_i)(H_i\tilde x_i^++v_i)^T],\nonumber
\\
&=H_i\mathrm{E}[\tilde x_i^+\tilde x_i^{+T}]H_i^T+\mathrm{E}[vv^T],\nonumber
\\
&=H_iP^+_iH_i^T+R_i.
\end{align}
From these, the similarity cost is defined as
%which are used to define $u_{p q}$ between $\hat z^+_{p}$ and $\hat z^+_{q}$:
\begin{align}
J_S&=\sum\limits_{p,q\in I,p\neq q}\exp (-au_{pq}),
\end{align}
where $u_{pq}\in\Re$ is
\begin{align}
u_{pq} & = (\hat z_{p}^+-\hat z^+_{q})^T{S^+_{pq}}^{-1}(\hat z^+_{p}-\hat z^+_{q})\label{eqn:U},
\end{align}
where $S^+_{pq}=S^+_{p}+S^+_{q}$.

Expanding \refeqn{U} with respect to the $p$-th system,
\begin{align}
u_{pq}=&\ 
(H_pK_p{\bf e}_p-\hat z^+_{q})^T
(H_pP^+_{p}H_p^T+R_p+S^+_q)^{-1}\nonumber
\\
&\ 
(H_pK_p{\bf e}_p-\hat z^+_{q}).
\end{align}
\newcommand{\Ibd}{\ensuremath{\mathbf{1}_{bd}}}

Next, we find the derivative of the similarity cost as follows.
Let $\Ibd\in \Re^{n\times m}$ be defined such that its $b,d$-th element is one and other elements are zero.
The partial derivative of $u_{pq}$ with respect to the scalar value at the $b,d$-th element of $K_p$, denoted as $K_{p,bd}$, is
\begin{align}
\deriv{u_{pq}}{K_{p,bd}}
=&\ 
(H_p\Ibd{\bf e}_p)^T
{S_{pq}}^{-1}
(H_pK_p{\bf e}_p-\hat z^+_{q})\nonumber
\\
&\ +
(H_pK_p{\bf e}_p-\hat z^+_{q})^T
\mathcal{S}
(H_pK_p{\bf e}_p-\hat z^+_{q})\nonumber
\\
&\ +
(H_pK_p{\bf e}_p-\hat z^+_{q})^T
{S_{pq}}^{-1}
(H_p\Ibd{\bf e}_p),\nonumber
\\
=&\ \{
2(H_p\Ibd{\bf e}_p)^T
{S_{pq}}^{-1}\nonumber
\\
&\ +(H_pK_p{\bf e}_p-\hat z^+_{q})^T
\mathcal{S}
\}
(H_pK_p{\bf e}_p-\hat z^+_{q}),\label{eqn:derivu}
\\
\deriv{u_{pq}}{K_{r,bd}}=&\ 0\quad \mbox{if } r\not\in\{p,q\},\label{eqn:derivu0}
\end{align}
where
\begin{align}
\mathcal{S}=&\ \deriv{{S^+_{pq}}^{-1}}{K_{p,bd}},\nonumber
\\
=&\ {S^+_{pq}}^{-1}
\deriv{\left(H_pP^+_{p}H_p^T+R_p+S^+_q\right)}{K_{p,bd}}
{S^+_{pq}}^{-1},\nonumber
\\
=&\ {S^+_{pq}}^{-1}
H_p
[(1-\beta_{0,p})(\Ibd H_pP_p^-+P_p^-H_p^T\Ibd^T)\nonumber
\\
&\ -\Ibd E_pK_p^T -K_pE_p\Ibd^T]
H_p^T
{S^+_{pq}}^{-1},\label{eqn:SS}
\end{align}
because
\begin{align}
&\deriv{\left(H_pP^+_{p}H_p^T+R_p+S^+_q\right)}{K_{p,bd}}
=
H_p
\deriv{P^+_{p}}{K_{p,bd}}
H_p^T\nonumber
\\
&=
H_p
[(1-\beta_{0,p})(\Ibd H_pP_p^-+P_p^-H_p^T\Ibd^T)\nonumber
\\
&\ \ \ -\Ibd E_pK_p^T -K_pE_p\Ibd^T]
H_p^T.\label{eqn:SSmidpart}
\end{align}
Then, \refeqn{SS} and \refeqn{SSmidpart} are substituted into \refeqn{derivu} or \refeqn{derivu0} to solve
\begin{align}
\label{eqn:JSK}
\deriv{J_S}{K_{p,bd}}=\ -a\sum\limits_{q\in I,q\neq p}\exp (-au_{pq})\deriv{u_{pq}}{K_{p,bd}}.
\end{align}

@@

%There are several benefits to choosing non-Kalman gains. The Kalman gain is suboptimal with respect to minimizing the linearized a posteriori covariance of the JPDAF. This issue is resolved with using the MUJPDAF, which is computationally comparable and is shown to consistently exhibit less RMS position error and state estimate uncertainty from simulations. The only drawback is that there exists a singularity, which is shown to be easily avoidable and has negligible effect on the filter performance.
%
%However, both the JPDAF and MUJPDAF suffer from coalescence when estimates are in close proximity. The C-JPDAF is derived in a more general sense (same assumptions as the JPDAF and MUJPDAF), which minimizes a weighted cost of state estimate uncertainty and a similarity index of the cluster of any number of estimates. By choosing this index inside the measurement space, the coalescence is more directly removed than prior work in~\cite{KauLovLee14}. To remove coalescence this way, there must be a trade-off between uncertainty increase and coalescence removal and powerful computational resources are also required.

Future work may take two directions: first, the computational requirements of the C-JPDAF make the algorithm infeasible in many scenarios; hence a suboptimal analytic solution that still removes coalescence would make the algorithm suitable for more applications. Second, all three algorithms may undergo further Monte Carlo simulations to show their performance in a variety of scenarios and applications.
These simulations may also serve as direct methods to find the weighting parameters of the C-JPDAF.

% Future work
	% Finding a suboptimal analytic solution to the C-JPDAF to lower the computational requirements
	% Running Monte Carlo simulations on both algorithms to show their performance in a variety of scenarios and applications
	% These simulations may serve as direct methods to find the weighting parameters of the C-JPDAF

>>>>

\title{\LARGE \bf
%Systematic Reduction of Uncertainty and Coalescence from JPDA Filtering
%Minimum Uncertainty JPDA Filtering and Advancements on Avoiding Coalescence
Minimum Uncertainty JPDA Filter and Coalescence Avoidance}
\author{Evan Kaufman and Taeyoung Lee$^*$% Thomas Alan Lovell,
 \thanks{Evan Kaufman and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{evankaufman, tylee\}@gwu.edu }}
%\thanks{Thomas Alan Lovell is a Research Aerospace Engineer at the Space Vehicles Directorate, Air Force Research Lab (AFRL), Albuquerque, NM. Email: {\tt\footnotesize afrl.rvsv@kirtland.af.mil }}
\thanks{$^*$This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}}

@@

Data association has been extensively studied with various applications in estimation when measurements are not necessarily originating from a single object.
We consider applications wherein multiple objects of interest enter the field of view of a sensor; however, the measurement origins are unknown.
To properly track these objects, we require estimation techniques that associate objects with measurements.
When the objects are in very close proximity, the association uncertainties grow, and an effective algorithm is necessary to maintain accurate estimations of the objects~\cite{KauLovLee14}.

@@

Alternatively with a soft decision technique such as the joint probabilistic data association filter (JPDAF), measurements are shared among the estimates. With the JPDAF, the likelihoods of association between measurements and estimates serve as weighting factors inside the measurement update portion of the filtering~\cite{JPDAF1},~\cite{TrackDataAssoc}.
The JPDAF is particularly advantageous in multi-object scenarios because when objects share measurements, the soft decisions prevent loss of information, which occurs with hard decision approaches.
%The a posteriori uncertainties of the estimates are changed because of an additional term representing the spread in the innovations; the Kalman gain serves as a close estimate to an optimal gain in the sense that in nearly minimizes this a posteriori gain as derived by the linearized equations of the JPDAF.
The JPDAF is based on the Kalman gain, which minimizes the posterior uncertainty of individual tracks.
However, the Kalman gain is not guaranteed to \emph{exactly} minimize the posterior uncertainties for data association of the JPDAF.
%The unnecessarily large uncertainty of the suboptimal Kalman gain serves as motivation to derive an optimal gain that minimizes the a posteriori uncertainty of the linearized JPDAF equations.

In this paper, we derive the optimal estimation gain that minimizes the magnitude of the posterior covariance matrix, and the resulting minimum uncertainty JPDAF is referred to as the MUJPDAF.

@@

Therefore, we propose a new coalescence-avoiding optimal JPDAF referred to as the C-JPDAF, which is a systematic approach to remove coalescence by minimizing the weighted sum of the uncertainty and a similarity index between estimates~\cite{KauLovLee14}.
The prior work covers the concept in simple cases, such that only two estimates are considered with a single measurement at each time step, making the algorithm infeasible in many realistic applications.
Therefore, we generalize the algorithm to handle any number of objects and measurements, as well as missed detections and measurements originating from extraneous clutter.
%Therefore we mature the algorithm to have the same assumptions as the JPDAF.
%Most importantly, there may be a variable number of measurements for a known number of estimates such that missed detections and false alarms are no longer an issue.

@@

During the flow update, the a priori (denoted with the superscript $-$) estimate $\hat x_{i_k}^-$ is found with \refeqn{xkp} and its a priori covariance $P_{i_k}^-$ is calculated from the last posterior (denoted with the superscript $+$) covariance $P_{i_{k-1}}^+$ for all $i$ as
\begin{gather}
%\hat x_{i_{k}}^- = f(\hat x_{i_{k-1}}^+),\\
P_{i_{k}}^- = F_{i_{k-1}} P_{i_{k-1}}^+ F_{i_{k-1}}^T + Q_{i_{k}}.
\end{gather}
These equations are applied between measurements to provide predictions of the states and their uncertainties.
% Equations for a priori state estimates and covariances

@@

Here we derive the optimal gain $K_i$ such that the posterior uncertainties are minimized with respect to the generalized JPDAF equations.

@@

Let the probability that object $i$ is not associated with any measurement be $\beta_{0,i}=1-{\sum\limits_{j} \beta_{ij}}$.
The resulting posterior covariance can be written as
%~\cite[Eq. D-32 and D-33]{TrackDataAssoc}
\begin{align}
\label{eqn:JPDAFCov}
P^+_{i}=&\ \beta_{0,i}P^-_{i}+(1-\beta_{0,i})P_i^c+\tilde P,
\end{align}
where $\tilde P\in\Re^{n\times n}$ is
\begin{align}
\tilde P=&\ K_i\parenth{{\sum\limits_{j} \beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}}{\bf{e}}_{i}^T}K_{i}^T,\label{eqn:tildeP}
\end{align}
and $P_i^c$ corresponds to the posterior covariance of object $i$ if only a single measurement serves to update this track~\cite{TrackDataAssoc}%, and it can be written as
%We can define $P_i^c$ without any assumptions on $K_i$ (i.e. $K_i$ is not necessarily the Kalman gain, so the well-known Kalman covariance update equations are not valid here) as~\cite[Eq. 4.2-12]{OptEst1}
\begin{align}
P^c_i=&\ (I-K_iH_i)P^-_i(I-K_iH_i)^T+K_iR_iK_i^T,\nonumber
\\
=&\ P^-_i-(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_i(H_iP^-_iH_i^T+R_i)K_i^T,
\label{eqn:GenCov}
\end{align}
(see~\cite{OptEst1}).
Substituting \refeqn{tildeP} and \refeqn{GenCov} into \refeqn{JPDAFCov},% and rearranging,
\begin{align}
P^+_{i}=&\ \beta_{0,i}P^-_{i}+(1-\beta_{0,i})[P^-_i-(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_i(H_iP^-_iH_i^T+R_i)K_i^T]\nonumber
\\
&\ +K_i\left({\sum\limits_{j} \beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}}{\bf{e}}_{i}^T\right)K_{i}^T,\nonumber
\\
=&\ P^-_{i}-(1-\beta_{0,i})(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_i\left((1-\beta_{0,i})S_i+{\sum\limits_{j} \beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}}{\bf{e}}_{i}^T\right)K_i^T,\nonumber
\\
=&\ P^-_{i}-(1-\beta_{0,i})(K_iH_iP^-_i+P^-_iH_i^TK_i^T)\nonumber
\\
&\ +K_iE_iK_i^T,\label{eqn:CovExpanded}
\end{align}
where the symmetric matrix $E_i=E_i^T\in\Re^{m\times m}$, defined as
\begin{align}
E_i=&\ (1-\beta_{0,i})S_i+{\sum\limits_{j} \beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}}{\bf{e}}_{i}^T.\label{eqn:E}
\end{align}
Note that $E_i$ is independent of $K_i$ and is invertible when $\beta_{0,i}\neq1$ since $S_i$ is positive-definite and
%may be calculated without knowledge of the gain matrix $K_i$, and is invertible because $P^-_i$ and $R_i$ are positive-definite and
$(\beta_{ij}e_{ij}e_{ij}^T-{\bf{e}}_{i}{\bf{e}}_{i}^T)$ is positive-semidefinite, as shown in the Appendix A. 
The case when $\beta_{0,i}=1$ corresponds with the $i$-th object \emph{not} being measured with full certainty, analyzed in Appendix B.

@@

Finally, \refeqn{GainK} is substituted into \refeqn{CovExpanded} to obtain
\begin{align}
%\begin{split}
%P^+_{i}=&P^-_{i}-(1-\beta_{0,i})^2(P^-_iH_i^TE_i^{-1}H_iP^-_i
%\\
%&+P^-_iH_i^TE_i^{-1}H_iP^-_i
%-P^-_iH_i^TE_i^{-1}E_iE_i^{-1}H_iP^-_i)
%\end{split}
%\\
P^+_{i}=&P^-_{i}-(1-\beta_{0,i})^2P^-_iH_i^TE_i^{-1}H_iP^-_i,
\end{align}
which may be simplified in two ways
\begin{align}
P^+_{i}=&P^-_{i}-K_iE_iK_i^T, \quad \mbox{or equivalently}\label{eqn:JPDAFPostCovSymmetricUpdate}
\\
P^+_{i}=&\left(I-(1-\beta_{0,i})K_iH_i\right)P^-_i.\label{eqn:JPDAFPostCovSimpleUpdate}
\end{align}
The proposed gain is compared with the Kalman gain explicitly in Appendix C.
In short, the differences between the MUJPDAF and the conventional JPDAF are shown in \refeqn{GainK} and \refeqn{JPDAFPostCovSymmetricUpdate} or \refeqn{JPDAFPostCovSimpleUpdate}. As the proposed optimal gain minimizes the posteriori uncertainties, the corresponding JPDA performs better, as illustrated by numerical examples later.

@@

The Matusita's similarity measure is defined between two Gaussian distributions.
Let $y_i$ be a random variable corresponding to the $i$-th system of set $I$ such that $y_i \sim \mathcal{N}[\hat y_i,{\mathbf P}_i]$, and let indices $p,q\in I$ such that $p\neq q$.
From~\cite{KauLovLee14}, the portion of the Matusita's similarity measure corresponding to the spread in the estimate means is given by
\begin{align}
\zeta_{pq}=\exp \{-a(\hat y_{p}- \hat y_{q})^T({\mathbf P}_{p}
+{\mathbf P}_{q})^{-1}(\hat y_{p}-\hat y_{q})\},\label{eqn:Mat2Est}
\end{align}
where $a>0$ shapes the similarity measure.

However, the distributions of more than two estimates may exhibit a nonzero overlap.
The similarity measure is changed to suit \emph{any} number of estimates by summing all combinations of Matusita's similarity measures, illustrated in Figure \ref{fig:SimMeas}, expressed in a general sense as
\begin{align}
\zeta=\sum\limits_{p,q\in I,p\neq q}\exp \{-a(\hat y_{p}- \hat y_{q})^T({\mathbf P}_{p}
+{\mathbf P}_{q})^{-1}(\hat y_{p}-\hat y_{q})\},
\end{align}
which is the summation of every similarity measure from \refeqn{Mat2Est} between all different Gaussian distributions $y_i$.
\begin{figure}
\centerline{
		{\includegraphics[width=\columnwidth]{GaussianDistOverlap1D.png}}
	}
\caption{The similarity index between three Gaussian distributions is a function the summation measures of overlapping regions of two distributions (green) or three distributions (brown). This concept is easily extended to multivariate distributions.
}\label{fig:SimMeas}
\end{figure}

@@

\paragraph*{Similarity Cost}
Any shared $z_j$ on estimate $i$ yields an innovation $e_{ij}$.
During the measurement update, this innovation typically has the net effect of drawing the measurement estimate towards $z_j$ if $\beta_{ij}$ is nonzero.
This occurs for all estimates and all measurements; coalescence results when measurement estimates are drawn towards common measurements.
Therefore, coalescence of the JPDAF or MUJPDAF occurs inside the measurement space (e.g. if a sensor provides ranges and bearings, these are in the measurement space as opposed to a Cartesian state vector inside the state space).
Contrary to~\cite{KauLovLee14} where the similarity index is in terms of state space variables, the coalescence avoidance presented in this paper takes place inside the measurement space to most directly remove the coalescence.
Let the posterior measurement estimate be $\hat z_i^+\in\Re^m$ and its innovation be $e_{i}^+\in\Re^m$ that corresponds with its true measurement $z_i\in\Re^m$ (although association is unknown) as
\begin{align}
\hat z_i^+&=H_i\hat x_i^+,
\\
e_{i}^+&=z_i-\hat z_i^+=(H_ix_i+v_i)-H_i\hat x_{i}^+=H_i\tilde x_i^++v_i,
\end{align}
where $\tilde x_i^+=x_i-\hat x_{i}^+$ denotes the error between the true state and the posterior estimate. The posterior innovation covariance $S^+_i\in\Re^{m\times m}$ is given by
\begin{align}
S^+_i&=\mathrm{E}[e_i^+e_i^{+T}]=\mathrm{E}[(H_i\tilde x_i^++v_i)(H_i\tilde x_i^++v_i)^T],\nonumber
\\
&=H_i\mathrm{E}[\tilde x_i^+\tilde x_i^{+T}]H_i^T+\mathrm{E}[vv^T],\nonumber
\\
&=H_iP^+_iH_i^T+R_i.
\end{align}
From these, the similarity cost is defined as
%which are used to define $u_{p q}$ between $\hat z^+_{p}$ and $\hat z^+_{q}$:
\begin{align}
J_S&=\sum\limits_{p,q\in I,p\neq q}\exp (-au_{pq}),
\end{align}
where $u_{pq}\in\Re$ is
\begin{align}
u_{pq} & = (\hat z_{p}^+-\hat z^+_{q})^T{S^+_{pq}}^{-1}(\hat z^+_{p}-\hat z^+_{q})\label{eqn:U},
\end{align}
where $S^+_{pq}=S^+_{p}+S^+_{q}$. Expanding \refeqn{U} with respect to the $p$-th system,
\begin{align}
u_{pq}=&\ 
(H_pK_p{\bf e}_p-\hat z^+_{q})^T
(H_pP^+_{p}H_p^T+R_p+S^+_q)^{-1}\nonumber
\\
&\times  
(H_pK_p{\bf e}_p-\hat z^+_{q}).
\end{align}
\newcommand{\Ibd}{\ensuremath{\mathbf{1}_{bd}}}

Next, we find the derivative of the similarity cost as follows.
Let $\Ibd\in \Re^{n\times m}$ be defined such that its $b,d$-th element is one and other elements are zero.
The partial derivative of $u_{pq}$ with respect to the scalar value at the $b,d$-th element of $K_p$, denoted as $K_{p,bd}$, is
\begin{align}
\deriv{u_{pq}}{K_{p,bd}}
=&\ 
(H_p\Ibd{\bf e}_p)^T
{S_{pq}}^{-1}
(H_pK_p{\bf e}_p-\hat z^+_{q})\nonumber
\\
&\ +
(H_pK_p{\bf e}_p-\hat z^+_{q})^T
\mathcal{S}
(H_pK_p{\bf e}_p-\hat z^+_{q})\nonumber
\\
&\ +
(H_pK_p{\bf e}_p-\hat z^+_{q})^T
{S_{pq}}^{-1}
(H_p\Ibd{\bf e}_p),\nonumber
\\
=&\ \{
2(H_p\Ibd{\bf e}_p)^T
{S_{pq}}^{-1} +(H_pK_p{\bf e}_p-\hat z^+_{q})^T
\mathcal{S}
\}\nonumber\\
&\times (H_pK_p{\bf e}_p-\hat z^+_{q}),\label{eqn:derivu}
\\
\deriv{u_{pq}}{K_{r,bd}}=&\ 0\quad \mbox{if } r\not\in\{p,q\},\label{eqn:derivu0}
\end{align}
where
\begin{align}
\mathcal{S}=&\ \deriv{{S^+_{pq}}^{-1}}{K_{p,bd}},\nonumber
\\
=&\ {S^+_{pq}}^{-1}
\deriv{\left(H_pP^+_{p}H_p^T+R_p+S^+_q\right)}{K_{p,bd}}
{S^+_{pq}}^{-1},\nonumber
\\
=&\ {S^+_{pq}}^{-1}
H_p
[(1-\beta_{0,p})(\Ibd H_pP_p^-+P_p^-H_p^T\Ibd^T)\nonumber
\\
&\ -\Ibd E_pK_p^T -K_pE_p\Ibd^T]
H_p^T
{S^+_{pq}}^{-1},\label{eqn:SS}
\end{align}
because
\begin{align}
&\deriv{\left(H_pP^+_{p}H_p^T+R_p+S^+_q\right)}{K_{p,bd}}
=
H_p
\deriv{P^+_{p}}{K_{p,bd}}
H_p^T\nonumber
\\
&=
H_p
[(1-\beta_{0,p})(\Ibd H_pP_p^-+P_p^-H_p^T\Ibd^T)\nonumber
\\
&\ \ \ -\Ibd E_pK_p^T -K_pE_p\Ibd^T]
H_p^T.\label{eqn:SSmidpart}
\end{align}
Then, \refeqn{SS} and \refeqn{SSmidpart} are substituted into \refeqn{derivu} or \refeqn{derivu0} to solve
\begin{align}
\label{eqn:JSK}
\deriv{J_S}{K_{p,bd}}=\ -a\sum\limits_{q\in I,q\neq p}\exp (-au_{pq})\deriv{u_{pq}}{K_{p,bd}}.
\end{align}

@@

%Future work may take two directions: first, the computational requirements of the C-JPDAF make the algorithm infeasible in many scenarios; hence a suboptimal analytic solution that still removes coalescence would make the algorithm suitable for more applications. Second, all three algorithms may undergo further Monte Carlo simulations to show their performance in a variety of scenarios and applications.
%These simulations may also serve as direct methods to find the weighting parameters of the C-JPDAF.
